comgen-outline

### 2017-06-27 paper/comgen-paper.Rmd
discuss relationship of mixture parameter to cue validity in discussion of prior expt

Generalizations about categories (i.e., *generic language*) have received substantial interest in psychology for their role in concept formation [@Gelman2004] and stereotype propogation [@Rhodes2012].
Generic language (e.g., *Birds fly.*) exhibits substantial flexibility in meaning and truth conditions as described above.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs. "Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties.
We do this by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} as well as the target probabilitiy that the speaker model seeks to convey $h$ in Eq. \ref{eq:S1}.
We show how these measurements systematically predict, via our model, endorsements of generic statements about familiar categories (Expt. 1b).

@@

We evaluate our family of RSA models, in addition to some ad-hoc non-Bayesian models, on these experimental data.
Because the ad-hoc models do not comprise a formalized alternative theory of endorsement and interpretation, but rather statistical descriptions of the data, we compare the ad-hoc models to the simplest RSA model on endorsement and interpretation, separately.
After presenting the results of Expts. 2 \& 3, we compare RSA models on their ability to jointly predict both endorsement and interpretation data simultaneously.

@@

## Experiment 1: Endorsing generalizations about categories

Any theory of generic language must explain their puzzling flexibility of usage with respect to prevalence.
That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: characteristic (e.g. \emph{Ducks have wings.}), minority (e.g. \emph{Robins lay eggs.}), striking (e.g. \emph{Mosquitos carry malaria.}), false generalization (e.g. \emph{Robins are female.}), and false (e.g. \emph{Lions lay eggs.}).
In additional to the canonical cases from the linguistics literature, we selected sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.

To compare the model to empirical truth judgments, we first measure the prior distribution over prevalence of these properties (Expt. 1a).
We hypothesize that this prior distribution encodes probabilities associated with deeper conceptual knowledge [e.g., of the kind discussed by @Prasada2013].
This would be one way in which our theory touches upon other psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
If, indeed, there are such things as different types of kind--property relations (e.g., *principled* v. *accidental relations*), we would expect the prevalence prior data to follow a multi-modal, mixture distribution where different modes or components of the prior are the results of the different types of relations.
As a simple test of this hypothesis, we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

After exploring the prevalence prior, we move on to the issue of primary theoretical interest: How well our *simple but underspecified* hypothesis accounts for endorsements of generic sentences (Expt. 1b).

### Experiment 1a: Measuring the Prevalence Prior for Categories

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, imagine your favorite kind of animal.
Then answer, "what percentage of that kind of animal is female?".
The answer is probably 50\%. 
Then ask yourself, "what percentage of that kind of animal lays eggs?".
Depending on what animal you thought of, the answer is probably either 50\% or 0\% (e.g., lions, tigers, and bears each have 0\% egg-laying members).

This decomposition of the prevalence prior $P(h)$ into a kind prior $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
We then ask whether a structured, prior model accounts better for this data than an unstructured model.

@@

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories (randomly sampled from a set corresponding to the generic sentences used in Expt. 1b (e.g. \textsc{robins, mosquitos}) and asked to generate five of their own.

A column then appeared to the right of the animal names with a property in the header (e.g., "lays eggs").
Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
Eight property--columns appeared in the table, and this whole procedure was repeated 2 times.
In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix).
The experiment can be viewed at \url{http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-2.html}.

@@

We begin by exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
We formalize this hypothesis using a simple, Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
The "unstructured", alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.

For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) or a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors values near 0: $\text{Beta}(1, 100)$.
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\alpha, \beta)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$. 
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with some mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \alpha = 1, \beta = 100) $$.^[
We use the mean / concentration parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \delta; \beta = (1 - \gamma) \cdot \delta$.
]
The unstructured hypothesis only represents a single component in the prior distribution $P(d) = \text{Beta} (d \mid \gamma, \xi)$.

We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account the flexibility of each model [@LW2014].
We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\theta$):

\begin{eqnarray}
\theta & \sim & \text{Uniform}(0, 1) \\
\gamma & \sim & \text{Uniform}(0, 1) \\
\xi & \sim & \text{Uniform}(0, 100) \\
\end{eqnarray}

Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property has its own parameters).

@@

roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
```
The Bayes Factor indicates the extent to which the data support one model over another.
The overall Bayes Factor in terms of Structured Model (S) over the Unstructured Model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
Indeed, the data strongly suggests the prevalence prior is structured.

It is possible that the data is, in fact, more structured than our simple two-component model. 
To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
This is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\theta$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\alpha, \beta)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(1, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the target category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
We could fit a more complex model to this data (i.e., one with three mixture components); however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density functions for prior distributions representing the prevalence of eight different features. Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')
    ggplot(m.gen.endorse.priors.posteriorPredictive, 
           aes( x = prevalence, color = src, lty = src))+
      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  coord_fixed()+
    xlab("Prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

@@

<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.  -->
<!-- Do a BDA to describe the data in a more compact form. -->
<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq. \ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).  -->
<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content. -->
<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the target category.  -->
<!-- Some properties have priors that are unimodal with low variance (e.g. \textsc{is female}); these properties are present in every kind in almost exactly the same proportion. The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.  -->
<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->

### Experiment 1b: Endorsing generic statements

>>>>

Generalizations about categories (i.e., *generic language*; e.g., *Birds fly.*) have received substantial interest in psychology for their role in concept and theory formation [e.g., @Gelman2004], stereotype propogation [@Rhodes2012], and motivation [@Cimpian2007], as well as many other facets of everyday cognition.
It is the premier case study of generalizations in language and has received the most attention from philosophers, linguists, and psychologists.

Any theory of generic language must explain its puzzling flexibility of usage with respect to prevalence.
That is, \emph{Mosquitos carry malaria} and \emph{Birds lay eggs} are reasonable things to say, but \emph{Birds are female} is not.
As a first test of our theory, we wish to explain the flexibility in endorsements of generics (e.g., "Birds lay eggs" vs. "Birds are female"; "Mosquitos carry malaria") in terms of the relevant prior knowledge about properties.
We do this by measuring the prior belief distribution over the relevant probabilities $P(h)$ used in Eq. \ref{eq:L0} as well as the target-category prevalence $h$ that the speaker model seeks to convey in Eq. \ref{eq:S1} (Expt. 1a).

<!-- The pragmatic speaker model $S_2$, Eq.~\ref{eq:S2}, is a model of truth judgments.  -->
We test our model on thirty generic sentences that cover a range of conceptual distinctions discussed in the literature [@Prasada2013]: characteristic (e.g. \emph{Ducks have wings.}), minority (e.g. \emph{Robins lay eggs.}), striking (e.g. \emph{Mosquitos carry malaria.}), false generalization (e.g. \emph{Robins are female.}), and false (e.g. \emph{Lions lay eggs.}).
In additional to the canonical cases from the linguistics literature, we selected sentences to elicit the full range of acceptability judgments (intuitively: "acceptable", "unacceptable", and "indeterminate") with low-, medium-, and high-prevalence properties.

To compare the model to empirical truth judgments, we measure the prior distribution over prevalence of these properties (Expt. 1a).
We hypothesize that these prior distributions encode probabilities associated with conceptual distinctions [@Prasada2013].
In particular, we hypothesize that different kind--property relations [e.g., *principled* v. *accidental relations*^[This is sometimes referred to as "statistical" relations.]; @Prasda2013] can be observed in the prevalence prior. 
If, in fact, the prevalence prior is one manifestation of deeper, conceptual knowledge, we would expect the prevalence prior data to follow a multi-modal, mixture distribution where there exist qualitatively modes or components of the prior, the results of the different types of kinds with respect to the property.
This is important because it is one way in which our formal theory connects to other, informal psychological accounts of generic language [cf., @Prasada2013; @Gelman2003; @Leslie2007].
As a simple test of this hypothesis---that the prevalence prior encodes conceptual knowledge---we compare a structured (i.e., mixture) model of the prior data to an unstructured one.

After having validated a measure of the prevalence prior, we consider the issue of primary theoretical interest: How well our *uncertain threshold* hypothesis accounts for endorsements of generic sentences (Expt. 1b).
In order to better understand the contribution of our theoretical framework, we evaluate alternative models that have either been previously analyzed in the generics literature or that are simpler forms of our *uncertain threshold* RSA model. 
To preview our results, we find that only our formulation of an uncertain threshold RSA model is able to account for the flexibility in generic endorsement.

@@

@@

## Experiment 1a: Measuring the Prevalence Prior for Categories

The prior $P(h)$ in Eq. \ref{eq:L0} describes the belief distribution on the prevalence of a given property (e.g. \textsc{lays eggs}) across relevant categories. 
To get an intuition for the kind of knowledge encoded in this belief distribution, consider the following thought experiment: You are on an alien planet and you come across your favorite kind of animal from Earth. Now try to predict whether or not that animal is female. To get an intuition for your subjective probability, ask yourself "What percentage of that kind of animal is female?".
The answer is probably 50\%. 
Now try to predict whether or not that animal lays eggs (or, "What percentage of that kind of animal lays eggs?").
Depending on what your favorite animal is, the answer is probably either 50\% or 0\% (e.g., if your favorite animal is a dog, there is a 0\% chance that it lays eggs)^[
The subjective probability may, in fact, be non-zero but very small. This would allow for the intuitive possibility of a dog that lays eggs potentially due to some strange generic mutation or the interaction of dog genetics with the alien environment. 
].

This decomposition of the prevalence prior $P(h)$ into a prior on kinds $P(k)$ and then a conditional probability of the prevalence of the feature given the kind $P(h \mid k)$ is one way to measure the prevalence prior $P(h) = \int_{k} P(h \mid k) \diff k$.
We measured this distribution by employing this technique empirically for the set of properties (e.g. \textsc{lays eggs, carries malaria}; 21 in total) used in our target sentences. 
We then ask whether a structured, prior model accounts better for this data than an unstructured model.

@@

On each trial of the experiment, participants filled out a table where each row was an animal category and each column was a property. 
Participants first were shown six animal categories randomly sampled from a set corresponding to the generic sentences used in Expt. 1b (e.g. \textsc{robins, mosquitos}) and asked to generate five of their own.

A column then appeared to the right of the animal names with a property in the header (e.g., "lays eggs").
Participants were asked to fill in each row with the percentage of members of each of the species that had the property by giving a number (e.g., "50\%").
Eight property--columns appeared in the table, and this whole procedure was repeated 2 times.
In total, each participant generated 10 animal names and reported on the prevalence of sixteen properties for 22 animals (their own 10 and the experimentally-supplied 12). 
<!-- For a full list of the properties, and generic sentences used in Expt. 1b, see Table 2 (Appendix). -->
The experiment can be viewed at \url{http://stanford.edu/~mtessler/experiments/generics/experiments/real-kinds/prior-2.html}.

@@

To create a larger set of properties, we reverse-code responses for five properties to create their corresponding negative properties (e.g., we create a property "doesn't have beautiful feathers" by subtracting from 100\% the responses for "has beautiful feathers").
In analyzing the prevalence prior data, we are primarily interested in exploring the hypothesis that the prior is structured as a result of deeper conceptual knowledge.
We formalize this hypothesis using a simple Bayesian mixture model. 
We test the simplest "structural" hypothesis, where there are two, qualitatively different components to the prior [e.g., if participants believe that some kinds have a causal mechanism that *could* give rise to the property, while kinds others do not; cf., @Griffiths2005].
The "unstructured" alternative hypothesis is that there is just a single distribution that gives rise to the prevalence prior data.

For the structural hypothesis, we assume the data was generated from one of two distributions: a distribution corresponding to those kinds with a stable causal mechanism that *could* give rise to the property ($\mathcal{D_{stable}}$) and a "transient cause" distribution corresponding to those kinds without a stable mechanism ($\mathcal{D_{transient}}$).
The "transient" distribution intuitively corresponds to accidental causes of the feature (e.g., a lion, who through some genetic mutation, reproduces by laying eggs).
We model this distribution as a Beta distribuition that heavily favors probabilities near 0: $\text{Beta}(\gamma = 0.01, \delta = 100)$.^[
Note that we use the alterantive mean $\gamma$ and concentration $\xi$ (or, inverse-variance) parameterization of the Beta distribution rather than the canonical shape (or pseudocount) parameterization for ease of posterior inference. The shape parameterization can be recovered using: $\alpha = \gamma \cdot \xi; \beta = (1 - \gamma) \cdot \xi$.
]
The "stable" distribution is modeled as a Beta distribution with unknown parameters $\text{Beta}(\gamma, \xi)$.^[
Because the Beta distribution is not defined at the points 0 and 1, we add $\epsilon$ to the 0 responses and round 1 to 0.99.
Adjusting 1 to $1- \epsilon$ leads to improper inferences for this model, as $1 - \epsilon$ is only likely under a highly right-skewed distribution; this would disproportionately influence the shape of $D_{stable}$. 
This problem does not appear for 0 being adjusted to $\epsilon$ because the "transient" distribution already expects such low values.
Similar results can be obtained by rounding 0 to 0.01. 
Alternatively, the "transient" distribution could be defined as a Delta distribution at 0, and 0 responses could remain in their raw form.
]
Finally, we assume that these two components combine with mixture weighting $\phi$ such that the data we observe is $$P(d) = \phi\cdot \text{Beta} (d \mid \gamma, \xi) + (1 -  \phi) \cdot \text{Beta}(d \mid \gamma = 0.01, \xi = 100) $$.
The unstructured alternative hypothesis assumes the data was generated by a single component in the prior distribution with unknown parameteres $P(d) = \text{Beta} (d \mid \gamma, \xi)$.

We test which hypothesis better accounts for the data by computing a Bayes Factor, which compares the relative explanatory power of each model while taking into account model flexibility [@LW2014].
We put the following priors over the latent parameters of each model (note that the unstructured model does not use $\phi$):

\begin{eqnarray}
\phi & \sim & \text{Uniform}(0, 1) \\
\gamma & \sim & \text{Uniform}(0, 1) \\
\xi & \sim & \text{Uniform}(0, 100) \\
\end{eqnarray}

Each property (e.g., "lays eggs", "carries malaria") is modeled independently (i.e., each property's prevalence prior has its own parameters).

@@

roundedBF1 = round(mean(marginal.prior.likelihoods$logBF)/ 10000)*10000
```

The Bayes Factor indicates the extent to which the data support one model over another.
The overall Bayes Factor in terms of structured model (S) over the unstructured model (U) for the full prevalence prior data set is approximately $\log BF_{SU} = `r roundedBF1`$, meaning that the structured hypothesis is approximately `r roundedBF1` orders of magnitude more likely than the unstructured hypothesis to account for the prevalence prior data.
Indeed, the data strongly suggests the prevalence prior is structured.

It is possible that the data is, in fact, more structured than our simple two-component model would allow. 
To see how well the structured model fits the prevalence prior data, we use Bayesian inference to infer the likely values of the parameters and then use the inferred parameters to generate new data.
This is called the *posterior predictive distribution* and is an important step in model validation. 
If the model is a good representation of the data, the posterior predictive data will align with the observed experimental data. 
We construct a posterior predictive distribution by "forward sampling" the model.^[
This can be described by the following algorithm: First, flip a coin weighted by $\phi$.
If it comes up heads, we then sample from the "stable" component: $\text{Beta}(\gamma, \xi)$.
If it comes up tails, we sample from the "transient" component: $\text{Beta}(0.01, 100)$.
We do this many times using the posterior distibution to generate a distribution over predicted prevalence ratings.
]

We implemented this statistical model using the probabilistic programming language WebPPL [@dippl].
To learn about the credible values of the parameters, we ran separate MCMC chains for each item, collecting 75,000 samples, removing the first 25,000 for burn-in.
Eight example prior distributions inferred using both the structured and unstructured models, together with the raw empirical distributions, are shown in Figure \ref{fig:generic-endorsement-priors-figure}.
There is a lot of diversity in the shapes of the distributions, which the structured model accounts for quite well.
One item that the structured model doesn't perfectly capture is the prior distribution over "lays eggs".
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the target category is fixed [e.g., estimating only the percentage of Robins that lay eggs; @Prasada2013]
]; our simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) is necessary to perfectly account for this item's data; however, we retain the imperfect simpler model for data-analytic ease going forward.

@@

```{r generic-endorsement-priors-figure, fig.width = 7, fig.height = 5, fig.cap="Cumulative density plots for prior distributions representing the prevalence of eight different features. Distributions are the posterior predictive distributions for the Structured and Unstructured prior models, as well as the raw empirical distribution. A completely uniform distribution would be represented as the y = x line."}
load('../analysis/generics-priors-posteriorPredictives.Rdata')
    ggplot(m.gen.endorse.priors.posteriorPredictive, 
           aes( x = prevalence, color = src, lty = src))+
      #geom_density(aes(y = ..scaled..), adjust = 1, size = 1)+
    #scale_fill_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    stat_ecdf(size = 1)+
    scale_color_manual(values = c("#636363", "#d7191c", "#2b83ba"))+
    scale_alpha_manual(values = c(0.6, 0.4, 0))+
    facet_wrap(~Property, nrow = 2)+
    scale_linetype_manual(values = c(1, 4, 3))+
    scale_x_continuous(breaks = c(0, 1), limits= c(0, 1))+
    scale_y_continuous(breaks = c(0, 1), limits= c(0, 1))+
  coord_fixed()+
    xlab("Prevalence") +
    ylab("Cumulative probability density")+
    theme(legend.position = "bottom", legend.title = element_blank())

@@

### Discussion

The prevalence prior distribution $P_f(h)$ encodes beliefs about the prevalence (or, probabilities) of a feature $f$ across different kinds.
These distributions are structured and must be represented by a model with at least two distinct generative components: one corresponding to those kinds that only accidentally or transiently have the feature and one corresponding to those kinds with a stable causal mechanism that gives rise to the feature with some probability.

<!-- The knowledge encoded by the prevalence prior distribution is similar to another theoretical construct discussed in the generics literature: cue validity. -->

If prevalence is the "forward probability" (e.g., one's predictions about whether or not an entity will lay eggs after learning that the entity is a robin), the inverse probability---$P(k \mid f)$ (e.g., one's predictions about whether or not the entity is a robin, upon learning that it lays eggs)---is known as *cue validity*.
For example, if one learns that an entity carries malaria, that entity is probably a mosquito because only mosquitos carry malaria; hence "carrying malaria" has high cue validity for mosquitos.

A natural proposal is that endorsements for generic language have to do with cue validity.
This possibility has been investigated empirically, and in fact, cue validity is highly correlated with generic endorsement [@Khemlani2012].
However, cue validity has some empirical and theoretical issues.
Empirically, cue validity is not a necessary criteria for generic endorsement (e.g., *Dogs have four legs*).
Theoretically, it's not obvious why cue validity would be part of the semantic content of generics.
If generics are for conveying generalizations and supporting prediction, listeners would be far better suited to have information that supports prediction about features given categories, not categories given features.
<!-- , since knowledge of cue validity requires knowledge of the kind whereas the forward-probability (prevalence)  can be computed only based on the feature. -->
<!-- ^[ -->
<!-- As a simple demonstration, imagine we've just discovered a new kind of animal called a fep. -->
<!-- It should be easy to estimate the prevalence of being female among feps (probably 50\%) even without any knowledge of feps.  -->
<!-- However, if you learn in another context that a particular entity is green, it's impossible to estimate the cue validity of being green for feps -->
<!-- that it's easy to estimate the prevalence of being female among  -->
<!-- ] -->

However, we shouldn't throw away the possibility that distributional information about the property is relevant. 
The mixture parameter $\phi$ in the prevalence prior distribution can be seen as a generalization of cue validity. 
Recall that $\phi$ is the weighting between the two generative components of the prevalence prior (i.e., the stable cause distribution $\mathcal{D_{stable}}$ and the transient cause distribution $\mathcal{D_{transient}}$).
If there is a finite number of kinds in the prevalence prior for a feature, and one knows the prevalence of the feature for each kind, then the cue validity of that feature for a particular kind is encoded in the prevalence prior, in that it can be derived via Bayes' Rule:
$$ P(k \mid f) = \frac{P(f \mid k) \cdot P(k)}{\sum_{k' \in K} P(f \mid k') \cdot P(k')} $$

Alternatively, if the number of kinds in prior is not fixed (e.g., if it is the product of a generative model of kinds), cue validity is not longer defined (or, it is zero for all kinds). 
This is for the same reason that for a continuous probability distribution, the probability of any particular number is zero. 
For example, consider the cue validity of "having wings" for \textsc{robins}: $P(\text{robin} \mid \text{has wings})$.
The feature of "having wings" is somewhat diagnostic for the category of \textsc{birds}, but there are many kinds of birds and the feature is not particularly diagnostic for anyone of them. 
At the same time, the mixture parameter for the distribution over the prevalence of "having wings" is still relatively small, since it represents information about the distribution and not one particular kind.
This is an important point of departure in our work from previous work.

<!-- The prevalence prior distribution, on the other hand, does not require that the set of categories be fixed.  -->
<!-- It in fact may be one dimension of a higher-dimesional generative model of kinds and properties. -->
<!-- Cue validity is conceptually related to the mixture parameter $\phi$ of the prevalence prior. -->
<!-- However, cue validity requires knowledge of the target category $k$ -->

<!-- For example, suppose there are 10 possible kinds and 3 of them belong the stable cause distribution and 7 belong to the transient cause distribution.  -->
<!-- Say we observe the feature and want to know what the probability that the entity is of a particular kind that we know to be of the stable distribution.  -->
<!-- If we know the prevalence given each distribution (i.e, $P(f \mid k_{stable})$ and $P(f \mid k_{transient})$). -->

<!-- For simplicity, assume that each component corresponds to a single probability (i.e., a single prevalence value) as opposed to a distribution. -->
<!-- Thus, $\mathcal{D_{stable}} = P(f \mid \mathcal{D_{stable}}) = p_{stable}$ -->

<!-- $n_{stable} n_{transient}$ -->

<!-- Previous studies have found cue validity to be correlated with generic endorsement [@Khemlani2012], though it's role in generic meaning is controversial [@Leslie2007; @Leslie2008]. -->
<!-- In empirical studies of generic language, however, it is often empirically measured [@Khemlani2012]. -->
<!-- For this analysis, we measured cue validity using a free production paradigm, following @Cree2006. -->
<!-- Participants ($n = 50$) were supplied with a feature (e.g., "X lays eggs") and asked to generate a kind (e.g., "what do you think X is ?"). -->
<!-- For a detailed discussion of the results of this experiment and comparison to other measurements of cue validity, see Appendix B. -->
<!-- To process the priors data, we discretize the prevalence judgments to 12 discrete bins: $\{[0-0.01), (0.01-0.05), (0.05-0.15), (0.15-0.25),  ..., (0.75-0.85), (0.85-0.95), (0.95-1]\}$, and look at the counts within each bin, after doing add-1 Laplace smoothing, as the relative probability of that prevalence.  -->
<!-- Do a BDA to describe the data in a more compact form. -->
<!-- We can explore how the underspecified-threshold listener model $L_{0}(x , \theta \mid u)$ (Eq. \ref{eq:L0}) interprets generic utterances with these priors on prevalence (Figure \ref{fig:commongenerics}a, insets).  -->
<!-- The prior beliefs over the prevalence of the property, $P(h)$, can also be interpreted as the pragmatic listener's posterior upon hearing the null utterance, because the null utterance has no information content. -->
<!-- We see the interpretation of the generic is quite variable across our empirically measured priors. -->
<!-- For instance, in the case of \textsc{carries malaria}, the prior is very left-skewed; with this prior, the threshold $\theta$ can plausibly be very low because high prevalence is unlikely. -->
<!-- Properties like \textsc{doesn't attack swimmers} are very right-skewed; with this prior, not many thresholds lead to a substantial update in beliefs, and so the generic is unlikely to be used by speaker $S_1$ unless the property is practically-universal within the target category.  -->
<!-- Some properties have priors that are unimodal with low variance (e.g. \textsc{is female}); these properties are present in every kind in almost exactly the same proportion. The model  and thus are too obvious and certain to allow for an informative generic utterance: The posterior is not very different from the prior.  -->
<!-- With $P(x)$ now empirically established, we can test if our speaker model predicts human truth judgments of generic statements about these properties. -->

## Experiment 1b: Endorsing generic statements
